---
title: "Alcohol Consumption"
author: "Mario Alonso Rodriguez & Raju Adhikari"
date: "October 6th, 2016"
output: pdf_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
### First, let's load all the packages that are needed
library(dplyr)
library(ggplot2)
library()
```

## Data

This is an assignment that utilizes fivethirtyeight.com's dataset on alcohol consumption in the world. This data is taken from the World Health Organization.  

```{r Drinks, message=FALSE, warning=FALSE}
### Load the raw data from fivethirtyeight's Github
Drinks <- read.csv('https://raw.githubusercontent.com/fivethirtyeight/data/master/alcohol-consumption/drinks.csv')

### A simple summary of descriptive statistics of all the dataset
summary(Drinks)

### The means of all the variables in the dataset
for (i in 1:length(names(Drinks))) {
    Drinks[, i] %>%
    mean() %>%
    round(digits = 1) %>%
    paste(names(Drinks)[i], ., '\n') %>%  cat() }

### Std deviation of all the variables 
for (i in 1:length(names(Drinks))) {
    Drinks[, i] %>%
    sd() %>%
    round(digits = 1) %>%
    paste(names(Drinks)[i], ., '\n') %>%  cat() }


```

## Histograms

Histograms are really usefull to look at the distribution of the data

```{r histograms}
### Distribution of beer consumption
hist(Drinks$beer_servings,
     main = 'Beer consumption',
     xlab = 'Number of bottles of beer consumed in 2010')

### Distribution of spirit consumption
hist(Drinks$spirit_servings,
     main = 'Spirit consumption',
     xlab = 'Number of spirit shots consumed in 2010')

### Distribution of wine consumption
hist(Drinks$wine_servings,
     main = 'Wine consumption',
     xlab = 'Number of wine glasses consumed in 2010')
```

## Transformation of the data

Seems like most of the countries consumed less than 50 of each in 2010. Let's unskew the distributions. 

```{r transformation}

