---
title: "Diamonds"
author: "Raju Adhikari & Mario Alonso Rodriguez"
date: "October 6th, 2016"
output: pdf_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
### Loading the packages necessary for this assignment
library(dplyr)
library(ggplot2)
```

## Data

First, we have to select a dataset from the ones already preloaded in R

```{r Data, echo=TRUE}
### Listing the in-built dataset from R
data()

### Loading the dataset diamonds and obtaining its description
data(diamonds)
? diamonds

### Listing all the variables that the dataset contains
names(diamonds)

### Getting a descriptive summary of the variables in the dataset
summary (diamonds)
```

## Histogram

A histogram of price variable shows the number of diamonds at different price level

```{r histogram, echo=TRUE}
#### Create the histogram
hist(diamonds$price)

hist(diamonds$price,
     main = 'Diamonds at Different Price Levels',
     xlab = 'The price of the diamonds')
```

## Statistics

A series of commands will show us the different descriptive statistics to analyze the data

```{r descriptive stats, echo=TRUE}
### Finding the mean, one of the main measures of central tendency
mean(diamonds$price, na.rm = TRUE)
mean(diamonds$depth, na.rm = TRUE)
mean(diamonds$carat, na.rm = TRUE)
mean(diamonds$table, na.rm = TRUE)
mean(diamonds$x, na.rm = TRUE)
mean(diamonds$y, na.rm = TRUE)
mean(diamonds$z, na.rm = TRUE)

### Finding the standard deviation for price variable
sd(diamonds$price)
```

## Tables

 A Crosstab shows how two variables are related
 
```{r crosstab, echo=TRUE}
### Crosstab shows that color and cut are roughly equally distributed
table(diamonds$cut, diamonds$color)

```

Please find the other part of this assignment on this link

[Drinks](https://github.com/marioalonsorodriguezv/Assignment1/blob/master/AlcoholConsumption.Rmd)
 